---
title: "Report"
author: "Your Name Here"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
met_area <- read.csv("output/met_area.csv")
```

## Introduction

A paragraph to introduce the research question

# Data and Methods

A couple of paragraphs to describe where the different data come from and how they were processed and to describe the method of analysis.

Here is a template code chunk for producing a figure. Be sure to change the name of the code chunk if you copy and paste it.

## Analysis

Show how the key independent and dependent variables are distributed. Use graphical techniques to show the bivariate relationship of interest and then show multivariate model results and interpret them. 

```{r figuretemplate, echo=FALSE, fig.cap="A Caption"}
#code (e.g. plot, hist, barplot, boxplot) to produce the figure
```

```{r regression_template, echo=FALSE, results='asis'}
#obviously these are not the models you want



```

## Conclusions

A paragraph to summarize the findings.