---
title: "Report"
author: "Your Name Here"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(stargazer)
met_area <- read.csv("output/met_area.csv")
```

## Introduction

A paragraph to introduce the research question

# Data and Methods

A couple of paragraphs to describe where the different data come from and how they were processed and to describe the method of analysis.

Here is a template code chunk for producing a figure. Be sure to change the name of the code chunk if you copy and paste it.

## Analysis

Show how the key independent and dependent variables are distributed. Use graphical techniques to show the bivariate relationship of interest and then show multivariate model results and interpret them. 

```{r figuretemplate, echo=FALSE, fig.cap="A Caption"}
#code (e.g. plot, hist, barplot, boxplot) to produce the figure
```

```{r regression_template, echo=FALSE, results='asis'}
#make some models
model1 <- lm()
model2 <- lm()
model3 <- lm()

#change type to "text" for inline test output, change back to "latex" for knitting to PDF
stargazer(model1, model2, model3,
          type="latex",
          keep.stat=c("n","rsq"),
          star.cutoffs = c(0.05,0.01,0.001),
          covariate.labels = c("Covariate labels here"),
          dep.var.labels.include = FALSE,
          dep.var.caption="White-Black SEI Difference",
          title = "Your caption here",
          notes.append=TRUE,
          notes.align="l",
          notes=c("Some notes","Some more notes"),
          header=FALSE)
```

## Conclusions

A paragraph to summarize the findings.