---
title: "Report"
author: "Your Name Here"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
met_area <- read.csv("output/met_area.csv")
#check for texreg package
if(!require("texreg")) {
  install.packages("texreg")
  library(texreg)
}
```

## Introduction

A paragraph to introduce the research question

# Data and Methods

A couple of paragraphs to describe where the different data come from and how they were processed and to describe the method of analysis.

Here is a template code chunk for producing a figure. Be sure to change the name of the code chunk if you copy and paste it.

## Analysis

Show how the key independent and dependent variables are distributed. Use graphical techniques to show the bivariate relationship of interest and then show multivariate model results and interpret them. 

```{r figuretemplate, echo=FALSE, fig.cap="A Caption"}
#code (e.g. plot, hist, barplot, boxplot) to produce the figure
```

```{r regression_template, echo=FALSE, results='asis'}
#make some models
model1 <- lm()
model2 <- lm()
model3 <- lm()

#to print to screen replace texreg with screenreg
texreg(list(model1, model2, model3),
       caption="Your caption here",
       #custom.coef.names = c("Covariate labels here"), #uncomment to add nice labels to independent variables
       digits = 3,
       caption.above=TRUE, 
       include.rsquared=TRUE,
       include.adjrs=FALSE,
       include.nobs=TRUE,
       include.rmse=FALSE,
       custom.note ="%stars.\nNotes: Some notes.")
```

## Conclusions

A paragraph to summarize the findings.